\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-05-14 fluB.tex
Add link to GH repo for data availability.
Fix #20 for now.

where $p(A_i)$ is the frequency of allele $A_i$ at locus A, $p(B_j)$ is the frequency of allele $B_j$ at locus B and $p(A_i B_j)$ is the frequency of haplotype $A_i B_j$.
D' is inflated when some haplotypes are not observed \textit{e.g.} when the minor allele frequency is low.
We find that D' is almost uniformly high across the influenza B virus genome and close to 1.0 for almost any pair of polymorphic loci.
This is because most amino acid alleles in the dataset exist transiently, meaning that they don't get a chance to reassort and we only observe them within the backgrounds of more persistent alleles, which D' quantifies as complete LD.
We think that metrics related to $r^2$, like $\chiSq$, perform much better on temporal data such as ours in finding associations between alleles and are easier to interpret.

>>>>

where $p(A_i)$ is the frequency of allele $A_i$ at locus A, $p(B_j)$ is the frequency of allele $B_j$ at locus B and $p(A_i B_j)$ is the frequency of haplotype $A_i B_j$.
D' is inflated when some haplotypes are not observed \textit{e.g.} when the minor allele frequency is low.
We find that D' is almost uniformly high across the influenza B virus genome and close to 1.0 for almost any pair of polymorphic loci.
This is because most amino acid alleles in the dataset exist transiently, meaning that they don't get a chance to reassort and we only observe them within the backgrounds of more persistent alleles, which D' quantifies as complete LD.
We think that metrics related to $r^2$, like $\chiSq$, perform much better on temporal data such as ours in finding persistent associations between alleles and are easier to interpret.

\subsection*{Data availability}
Python scripts used to process trees and sequences, as well as their output are publicly available at:
\\https://github.com/evogytis/fluB/tree/master/data.
